---
title: "Assignment 4: LHS Sensitivity Analysis"
author: "Bri Baker, Wylie Hampson, Shale Hunter"
date: "4/21/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(pse)
```

## Setup

```{r source}
# Source the conductance function that we created
source(here("R", "atm_conductance.R"))
```

```{r test}
# Test to make sure the function is working properly
atm_conductance(height = 1000, windspeed = 250)
```

## Paramater Sensitivity Analysis

Here we will perform sensitivity analysis on `height`, `windspeed`, `k_d`, and `k_0`. `windspeed`, `k_d`, and `k_0` are all normal distributions (values are calculated using standard deviations around a mean), and height is a uniform distribution between 9.5 and 10.5 m. 

```{r param_dist}

# define parameters to test
factors <- c("height", "k_d", "k_0", "windspeed")

# define sample size
nsets <- 100

# set distributions for parameters above
q <- c(
  "qunif", # height
  "qnorm", # k_d
  "qnorm", # k _0
  "qnorm"  # windspeed
)

q.args <- list(
  list(min = 950, max = 1050),  # height
  list(mean = 0.7, sd = 0.007), # k_d
  list(mean = 0.1, sd = 0.001), # k_0
  list(mean = 250, sd = 30)     # windspeed
)

```

```{r LHS}

# run LHS and generate samples
sens_conductance <- LHS(NULL, factors, nsets, q, q.args)
sens_pars <- get.data(sens_conductance)
head(sens_pars)

```

```{r conductance}

# run model for parameters generated
conductance_values <- atm_conductance(height = sens_pars$height, 
                                      k_d = sens_pars$k_d,
                                      k_0 = sens_pars$k_0,
                                      windspeed = sens_pars$windspeed)

conductance_values

```

```{r link}

# make output matrix
conductance_values <- as.matrix(conductance_values)

# link LHS object (sens_conductance) to outputs
sens_conductance <- pse::tell(sens_conductance, 
                              t(conductance_values),
                              res.names = "Atmospheric Conductance")
```


## Plot Parameter Sensitivity


```{r box}

# make output df
conductance_values <- as.data.frame(conductance_values)

# plot as boxplot (conductance est + uncertainty)
ggplot(conductance_values, aes(y = V1)) + 
  geom_boxplot() +
  labs(
    y = "Atmospheric conductance (cm/s)",
    title = "Variation in predicted atmospheric conductance outputs",
    caption = "Conductance values modeled based on \nparameters estimated by LHS analysis."
    ) +
  theme(plot.title = element_text(hjust = 0.5))

```

```{r scatter}

# plot conductance vs params
pse::plotscatter(sens_conductance, col = "blue", cex = 5)

```

```{r prcc}

# estimate partial rank correlation coefficients
pse::plotprcc(sens_conductance)

```

```{r prcc_view}

# show prcc for params
sens_conductance$prcc

```


## Discussion

Our results suggest that all four parameters (`height`, `windspeed`, `k_d`, and `k_0`) affect atmospheric conductance (all have Partial Rank Correlation Coefficients > 0.60), but within the uncertainty range provided windspeed has the strongest correlation with the output (PRCC = 0.99). Because windspeed has such high correlation with modeled atmospheric conductance, uncertainty in this parameter would lead to less reliable outputs. Thus, efforts to reduce uncertainty in aerodynamic conductance estimated should focus on improving certainty in windspeed measurements.

Plant water conductance is highly sensitive to variation in windspeed which indicates that local weather patterns are important to plant water use. Insofar as climate change can influence local weather (including wind patterns), plant water use may be sensitive to climate change. However, day to day variation in windspeed drives local plant water use on a finer scale.


